log hyperparameter optimization

### 2020-04-03 simulation_study/hpoptimization/README.Rmd
config files SCDD

>>>>

01.04
nn-2-layer retry r-1 
```{r}
cons <- expand.grid(c = classifier[5], fe = c("tfidf", "doc2vec"), d = d, stringsAsFactors = FALSE)

nn_test <- sprintf("./cart_hyper_run_asrnn.py hyper-active -t 5-00:00:00 -m %s -b double -e %s -q max -d %s -r 2", cons$c, cons$fe, cons$d)
write.table(nn_test, file = "scripts/one/nn_test.txt", sep="\t", quote = FALSE, row.names = FALSE)

names(nn_test) <- c("7891389", "7891390", "7891391", "7891392", "7891393", "7891394", "7891395", "7891396", "7891402", "7891407", "7891408", "7891411")
# ./cart_hyper_run_asrnn.py hyper-active -t 55 -m nn-2-layer -b double -e doc2vec -q max -d wilson -r 2 # 7886988, 
#./cart_hyper_run.py hyper-active -t 55 -m nn-2-layer -b double -e doc2vec -q max -d ace -r 2 # 7883466
# ssh tcn560
# top 
```

```{r}
# cancel all logistic 4-1 sets 
#  7873347, 7873448, 7873460, 7873464, 7873469, 7873473
hpsets["LCTD", , "four"] <- 2
```

03.04.2020
```{r}
# svm d2v one are done! 
hpsets["SCDD",, "one"] <- 2
```
